---
title: "Online Shopping Behavior"
author: "Chirapa Muadchan, Htein Linn Thar, Natnicha Palakawong, PIN-JUI-HUANG"
date: "11/7/2019"
output: 
  ioslides_presentation:
    css: styles.css
    fig_width: 7.5
    fig_height: 5.5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

options(scipen = 999) ##scientific notation suppresser
```

```{r}
library(dplyr)
library(kableExtra)
library(caret) #train
library(ggplot2)
library(scales)
library(nnet)
library(graphics) #pair for cor coef
library(magrittr) 
library(GGally)
library(forcats)
library(gmodels)
```

```{r}
shop = read.csv('online_shopping.csv')
```
## Introduction

The internet shopping particulary in business to consumer(B2C) has risen and online shopping has become more popular to many people.

<b>Objective</b><br>

- To understand the consumers' perception and shopping behavior toward online retail<br>
- To find out the buying pattern of consumers while shopping online<br>
- To study relevance between the consumer buying decision with respect to price, time, demography and so on<br>
- To make the successful business strategy knowledge of consumer perception<br>

## Dateset

Primary data is to be collected from the respondents with the help of a structured questionnaire<br>
Sample Size: 117 parcitipants<br>
Method: Convenience sampling<br>
Tool: Quentionnaire<br>
Techinique: Online Survey - Social media and friends<br>
Independent Variable: age, gender, marital status, occupation and income<br>
Dependent Variable: variables related to consumer behaviors<br>


## Data Visualization

```{r, include=FALSE}
Female <- round((nrow(shop[shop$Gender == 'Female', c("Status", "Shop_Online")])/nrow(shop))*100, 3)
Male <- round((nrow(shop[shop$Gender == 'Male', c("Status", "Shop_Online")])/nrow(shop))*100, 3)
slices1 <- c(Female, Male)
lbls1 <- paste(c("Female", "Male"), "\n", slices1, "%", sepd="")
g1 <- pie(slices1, col=c("purple","orange"), labels=lbls1, main="Gender Distribution")

```


```{r, include=FALSE}

slices2 <- c(22,35,38,64,26)
lbls2 <- paste(c("Makeup", "Home Electronic", "Travelling", "Clothing", "Ticket"),slices2)
g4 <- pie(slices2, col=c("purple","orange","green","pink","blue"), labels=lbls2, main="Top 5 items that people buy online the most")


```


```{r, include=FALSE}
counts1 <- table(shop$Status)
g2 <- barplot(counts1, main="Maritual Status Distribution", col = 'orange',
   ylab="Number of participants", las = 2 )

```

```{r, include=FALSE }
data = shop[,c(2,9)]
counts2 <- table(data$Gender, data$Shopping_TimeSpent_Monthly)

g3 <- barplot(counts2, main="Distribution by  and Gender", ylab = "Count",
   col=c("darkblue","red"), las = 2,
   legend = rownames(counts2))
 

```


```{r}
attach(shop)
par(mfrow = c(2,2))
barplot(counts2, main="Distribution by Online Shoping frequency\n and Gender", ylab = "Count",
   col=c("darkblue","red"), las = 2,
   legend = rownames(counts2))
barplot(counts1, main="Marital Status Distribution", col = 'orange',
   ylab="Number of participants", las = 2 )
pie(slices1, col=c("grey","red"), labels=lbls1, main="Gender Distribution")
pie(slices2, col=c("purple","orange","green","pink","blue"), labels=lbls2, main="Top 5 items that people \n buy online the most")


```


## Chi-square Test{.normalFont}
To test if there is a statistically significant correlation between gender and their online shopping behavior, we can use a chi-squared test of independence. 

Hypothesis<br>
H~0~ : Gender and their online shopping behavior are independent<br>
H~a~ : Gender and their online shopping behavior are dependent
```{r}
table(shop$Gender,shop$Shop_Online)
chisq.test(table(shop$Gender,shop$Shop_Online),correct=FALSE)
```
Since p-value is greater than 0.05, there is no significant evidences to say that there is difference between male and female related to their behavior toward online shoping.

## Chi-square Test{.normalFont}
To test if there is a statistically significant correlation between privacy concern and people behvior on online shopping, we can use a chi-squared test of independence. 

Hypothesis<br>
H~0~ : Privacy concern and online shopping behavior are independent<br>
H~a~ : Privacy concern and online shopping behavior are dependent

```{r}
table(shop$Privacy_Concern,shop$Shopping_Preferrence)
chisq.test(table(shop$Privacy_Concern,shop$Shopping_Preferrence),correct=FALSE)
```

Since p-value is greater than 0.05, there is no enough evidence to conclude that privacy concern affect the online shopping behavior of people.


## Correlation Between the Variables
```{r, fig1, fig.height=3, fig.width=5}
d = shop[,c(1,3,8,10)]
d1 = na.omit(d)
d1 %>%
  select(Age, Monthly_Income, Browsing_Time, Shopping_MoneySpent_Monthly) %>%
## Overwrite the original name of variables
  set_colnames(c("Age", "Income", "Browsing", "Spend")) %>%
  ggcorr(palette = "Spectral", label = TRUE, limits = FALSE, low = "darkred", mid = "orange", high = "green4", midpoint = 0.67, label_round = 2)
```

The Pearson correlation coefficient indicates a moderate __*linear*__ correlation between spending and monthly income.

## Linear Regression Model{.smaller}
<b>Model 1 : Shopping_MoneySpent_Monthly = Age + Monthly_Income + Browsing_Time</b>
```{r}
m1 = lm(Shopping_MoneySpent_Monthly~Age+Monthly_Income+Browsing_Time, d1)
summary(m1)

```

## Linear Regression Model{.smaller}
<b>Model 2  Shopping_MoneySpent_Monthly =  Monthly_Income</b>
```{r}
m2 = lm(Shopping_MoneySpent_Monthly~Monthly_Income, d1)
summary(m2)


```

## Compare model 1 and 2{.smaller}

```{r}
anova(m1,m2)

```
We compare these two models using anova. As can be seen, the p-vlaue is greater than 0.05,and we can say there is no difference between these two models. This means we just need one predictor which is Monthly_Income to predict the outcome of our model.


## Limitation

<b>External Validity</b><br>

- Online survey<br>
- Convinience sampling<br>
- Not representative<br>

<b>Internal Validity</b><br>

- Sample size was only 117<br>
- The age range was not diverse which would also affect IV such as income and marital status<br>
- Some of the participants didn't complete the survey<br>


## Conclusion

<b>Learning</b><br>

- Comprehensive idea of online consumer behavior<br>
- A strong relation exists between monthly income, occupation and purchase decision of respondents. <br>


<b>Future Research</b><br>

- Enhance sampling size to improve external validity<br>
- Choose random sampling instead of convience sampling to achieve diversity<br>

## References

- Kabacoff, Robert I. "Quick-R by DataCamp." 2017. Sitemap. 5 December 2019. <https://www.statmethods.net/graphs><br>

- "Chi-Square Test in R | Explore the Examples and Essential concepts!" 10 July 2019. Data Flair. 4 December 2019. <https://data-flair.training/blogs/chi-square-test-in-r/><br>

- Xie, Yihui. "Title slide." 12 May 2019. GitHub. 5 December 2019. <https://github.com/yihui/xaringan/wiki/Title-slide><br>

- Porras, Eladio Montero. "Linear Regression in R." 18 July 2018. Data Camp. 5 December 2019. <https://www.datacamp.com/community/tutorials/linear-regression-R>

